Paper_Figure

### 2023-10-29 paper_figure.Rmd
fig-adjustment

@@

P_ls = Obtain_Pls(W = W, max_time = 2^10)
rho = Rowwise_normalize(dat[,colnames(W)])
res = fast_calculate_multi_score(W = W, init_state = rho, P_ls = P_ls)
```
```{r}
# Plot knn graph
plot_knn_graph(affinity_m = W, label = cell_label, layout = visual_space)
```
```{r}
# Check Diffusion KL pattern for several genes
genes = c("Fcnb","Uchl4")
genes_label = c("localized","non_localized")
check_time = c(0,8,128,1024)
p = Visualize_score_pattern(res, genes = genes, label_class = genes_label, facet_class = NULL, add_point = check_time)

# Check Gene Diffusion on Cell graph by time
pl = lapply(genes,function(gene){
  FeaturePlot_diffusion(coord = visual_space,init_state = rho[gene,],P_ls = P_ls,check_time = check_time,gene_name = gene)
})
plot_grid(plotlist = pl,ncol = 1)
```

@@

df_auc = df_auc %>% filter(gt_set %in% c("Top100","CellMarkerDB")) %>% filter(!Method %in% "HighlyVariableGenes")
df_auc$Method <- with(df_auc, reorder(Method, -AUROC, FUN = median))
df_auc$gt_set <- factor(df_auc$gt_set,levels = c("CellMarkerDB","Top100"))
levels(df_auc$gt_set) = c("Criterion1 - CellMarkerDB","Criterion2 - MaxFC")
df_auc$Tissue = factor(df_auc$Tissue,levels = tissue_ls)
levels(df_auc$Tissue) = c("Bone Marrow","Pancreas","Lung")
# Create the plot
fig <- ggplot(df_auc, aes(x = Tissue, y = AUROC, fill = Method)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(AUROC, 2)), position = position_dodge(width = 0.85), vjust = -0.25, size = 2) +
  theme_minimal() +
  labs(x = "Tissue", y = "AUROC", fill = "Method") + coord_cartesian(ylim = c(0.5, 1)) +
  theme(legend.position = "bottom")  +  scale_fill_manual(values= coldef[names(coldef)%in%df_auc$Method]) + facet_wrap(~gt_set)

@@

df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))
method_vs = "lmd"
method_vs_set = c("wilcox_default","hotspot","marcopolo","semi","haystack")
```
```{r}
sub = do.call(c,lapply(method_vs_set,function(method){
  sub = c(which(df_benchmark[,method] <= 100 & df_benchmark[,method_vs] > 500),
          which(df_benchmark[,method] > 500 & df_benchmark[,method_vs] <= 100) )
  sub
}))
df_label_all = df_benchmark[unique(sub),c(method_vs,method_vs_set)]
df_label_all$'legend' = sapply(seq(nrow(df_label_all)),function(i){
  paste(paste(method_fullname[colnames(df_label_all)],df_label_all[i,],sep = ":"),collapse = "\n")
})
g = c("Cd19","Naaa","Mogat2","Tifa","Abca13","Zf12","Il2rb","Phgdh","Vpreb2","Fyb")
pl = lapply(g,function(x){
  FeaturePlot(tiss,features = x,order =TRUE) + annotation_custom(grob = grid::textGrob(df_label_all[x,"legend"], x = 1, y = 1, just = c("right", "top"),gp = grid::gpar(col = "red", fontsize = 10)))
})
fig = cowplot::plot_grid(plotlist = pl[as.numeric(t(matrix(1:length(pl),nrow = 2)))],ncol = length(method_vs_set))
ggsave(filename = "fig-ranking_comparison.png", plot = fig, width = 25, height = 10)
```
```{r}
pl_rank = lapply(method_vs_set,function(method){
  df_label = data.frame(df_benchmark[,c(method,method_vs)],label = rownames(df_benchmark))
  df_label[c(which(df_label[,method] <= 100 & df_label[,method_vs] > 500)),"color"] = sprintf("Favor by %s (rank <= 100)",method)
  df_label[c(which(df_label[,method] > 500 & df_label[,method_vs] <= 100) ),"color"] = sprintf("Favor by %s (rank <= 100)",method_vs)
  df_label$'color' = as.factor(df_label$'color')
  p = ggplot(df_label, aes(x=!!as.name(method), y=!!as.name(method_vs),color = color)) + geom_point(size = 1) + 
  scale_color_manual(values = c("red", "blue", "grey50"),
                     breaks = levels(df_label$'color')) + 
    geom_abline(intercept = 0, slope = 1, col = "grey", linetype = "dashed") + scale_x_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) +
    scale_y_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) +
    expand_limits(x = c(1, 10^4), y = c(1, 10^4)) +
    labs(x = paste0(method_fullname[method]," Rank"), y = paste0(method_fullname[method_vs]," Rank"), color = "Highlighted Genes") + theme_minimal() 
  # annotate gene labels
  # library(ggrepel)
  p = p + geom_text_repel(data = df_label %>% filter(!is.na(color)) %>% filter(label %in% g), aes(label=label),min.segment.length = unit(0, 'lines'),nudge_y = -0.5)
  p
})
pdf(width = 25,height = 5)
legend = get_legend(pl_rank[[1]] +  guides(color=guide_legend(direction="horizontal")))
prow = plot_grid(plotlist = lapply(pl_rank,function(x) x + NoLegend()), ncol = length(method_vs_set))
plot_grid(prow, legend, ncol = 1, rel_heights = c(1, .2))
dev.off()
```

@@

baseline = score_measure %>% filter(Method == "all genes") %>%.$DensityIndex
max_x = score_measure %>% filter(Method!="all genes") %>%.$TopGene %>% max()

fig = ggplot(score_measure %>% filter(Method!="all genes"), aes(x = TopGene, y = DensityIndex, color = Method, group = Method)) + geom_line(aes(linetype = Method)) + guides(linetype="none") + scale_color_manual(values= coldef[names(coldef)%in%score_measure$Method]) + geom_hline(yintercept = baseline, linetype = "dashed", color = "grey1", alpha = 0.6) + annotate("text", x = max_x, y = baseline, label = "All_genes", vjust = -1, color = "grey1")  + theme_minimal() + geom_text_repel(data = score_measure %>%  filter(Method!="all genes") %>% group_by(Method) %>% slice_head(n = 2) %>% slice_tail(n = 1), aes(label = Method), hjust = 0)
pdf(width = 8,height = 5)
fig
dev.off()
```

# Fig - Sensitivity Test
```{r}
## Rank Stability
score_df = read.table(paste0(path,tissue_name,"_different_knn.csv"),header = TRUE)
score_ranked <- data.frame(score_df) %>% mutate(across(everything(), rank))
base = "kNN5"
top_genes_list <- lapply(c(50,seq(100,1000,100)), 
                         function(x) head(score_ranked[order(score_ranked[,base]),], x))
average_ranks <- lapply(top_genes_list, function(top_genes) {
  colMeans(top_genes)
})
average_ranks <- data.frame(
  Top_Genes = c(50,seq(100,1000,100)),
  do.call(rbind, average_ranks)
)
average_ranks <- average_ranks %>% tidyr::pivot_longer(cols = -Top_Genes, names_to = "kNN", values_to = "Average_Rank")
average_ranks$kNN = as.numeric(gsub("kNN","",average_ranks$kNN))

fig = ggplot(data = average_ranks, aes(x = kNN, y = Average_Rank, group = Top_Genes)) +
  geom_line() +
  geom_point() + labs(x = "kNN", y = sprintf("Average Rank of Top # Genes\n (base on %s)",base)) + geom_vline(xintercept = 5, color="red", linetype="dashed") +
  theme_minimal() + facet_wrap(~Top_Genes,scales = "free",labeller = as_labeller(setNames(paste0("Top",unique(average_ranks$Top_Genes)),unique(average_ranks$Top_Genes)))) + NoLegend()
pdf(width = 8,height = 5)
fig
dev.off()
```
```{r}
## AUC stability
auc_df = read.table(paste0(path,tissue_name,"_sensitivity_auroc.csv"),header = TRUE)
auc_df <- auc_df %>% tidyr::pivot_longer(cols = -gt, names_to = "kNN", values_to = "AUC") %>% filter(gt %in% c("Top100","CellMarkerDB"))
auc_df$gt = factor(auc_df$gt); levels(auc_df$gt) = c("CellMarkerDB","MacFC(Top100)")
auc_df$kNN = as.numeric(gsub("kNN","",auc_df$kNN))
fig = ggplot(data = auc_df, aes(x = kNN, y = AUC), group = gt) +
  geom_line() +
  geom_point() + labs(x = "kNN", y = "AUROC") + facet_wrap(~gt, scales = "free") + 
  theme_minimal()
pdf(width = 6,height = 3)
fig
dev.off()
```

# Fig - Gene-Gene Colocolization HeatMap
```{r}
load("./marrow_result/module_result.rdata")
source("./LMD_function.R", echo = F)
library(RColorBrewer)
library(dplyr)
module_color = setNames(colorRampPalette(brewer.pal(12, "Paired"))(nlevels(gene_partition)),levels(gene_partition))
celltype_color = setNames(colorRampPalette(brewer.pal(9, "Set1"))(length(unique(cell_label))),unique(cell_label))

p = pheatmap(as.matrix(dist),
              annotation_col = data.frame(Module = gene_partition),
              cluster_rows = gene_hree, 
              cluster_cols = gene_hree,
              ann_colors = list(Module = module_color),
              treeheight_row = 0,
              col=colorRampPalette(c("firebrick3", "white"))(99),
              show_colnames = FALSE, 
              show_rownames = FALSE,
              annotation_legend = FALSE,
              # main = paste(distance_method,
              #              clustering_method,sep = "-"),
              silent = TRUE)
p = as.ggplot(p)
ggsave(filename = "fig-moduleheatmap.png", plot = p, width = 10, height = 10)
```
# Fig - Module Jaccard
```{r}
jaccard_index_pruned = jaccard_index[apply(jaccard_index,1,max) > 0.4,]
jaccard_index_pruned = jaccard_index_pruned[,apply(jaccard_index_pruned,2,max) > 0.4]

colnames(jaccard_index_pruned) = paste0("M",colnames(jaccard_index_pruned))
p = pheatmap(t(jaccard_index_pruned)[,names(sort(apply(jaccard_index_pruned,1,which.max)))],
         cluster_rows=FALSE, cluster_cols=FALSE, 
         scale = "none", 
         color = colorRampPalette(rev(c("firebrick3", "white")))(99),
         angle_col = 45,legend_title = "Jaccard Index",silent = TRUE,
         cellwidth = 15, cellheight = 10)
p = as.ggplot(p)
ggsave(filename = "jaccard_heatmap.png", plot = p, width = 5, height = 10)
```
```{r}
# # Bipartite Plot
# jaccard_thred = 0.4
# 
# library(igraph)
# library("grid") 
# library("gridExtra") 
# 
# df_edge <- as.data.frame(as.table(jaccard_index))
# colnames(df_edge) = c("from","to","weight")
# df_edge <- subset(df_edge, weight > jaccard_thred)
# df_edge$width = ifelse(df_edge$weight > 0.8,2,0.5)
# df_node = data.frame(name=c(names(module_color),names(celltype_color)),color = c(module_color,celltype_color))
# df_node$type = ifelse(df_node$name %in% names(module_color),TRUE,FALSE)
# 
# # Define specific color for module
# rownames(df_node) = df_node$name
# ct_module = names(which(apply(jaccard_index,2,max) > jaccard_thred))
# ct_subtype_module = c(4,5,6,30,39,42,43)
# ct_multype_module = c(2,13,19,33,36,54)
# cc_module = c(16,17,18,31)
# df_node[names(module_color),"color"] = "grey"
# df_node[ct_module,"color"] = "red"
# df_node[ct_multype_module,"color"] = "purple"
# df_node[ct_subtype_module,"color"] = "yellow"
# df_node[cc_module,"color"] = "green"
# 
# g <- graph_from_data_frame(df_edge, directed=FALSE, vertices=df_node)
# V(g)$shape <- ifelse(V(g)$type, "circle", "square")
# E(g)$color <- ifelse(E(g)$weight > 0.8, "red", "grey")
# l <- layout_as_bipartite(g, types=!V(g)$type)
# 
# plot(g, layout=l, vertex.size=2, vertex.label=ifelse(V(g)$type, V(g)$name, NA), vertex.frame.color = NA, asp=0.2, 
#      vertex.label.cex=0.5,
#      vertex.label.dist=-1,
#      vertex.label.degree=pi/2)
# 
# # Create Node Legend & Edge Legend
# color_label = c("green" = "cell cycle",purple = "multi cell type",red = "cell type",yellow = "cell subtype")
# df_node$subtype = color_label[df_node$color]
# 
# p <- ggplot(df_node %>% filter(type), aes(x = 0, y = 0,color = subtype)) + geom_point(size = 7) + scale_color_manual(values= setNames(names(color_label),color_label)) + theme_minimal() + labs(color = "Module Type") + theme(legend.direction="horizontal")
# grid.newpage()
# grid.draw(get_legend(p))
# 
# p <- ggplot(df_node %>% filter(!type), aes(x = 0, y = 0,color = name)) + geom_point(size = 7,shape = 15) + scale_color_manual(values= df_node %>% filter(!type) %>% pull(color,name)) + theme_minimal() + labs(color = "Cell Type") + theme(legend.direction="horizontal")
# grid.newpage()
# grid.draw(get_legend(p))
```
# Fig - Module TSNE
```{r}
pl_module = lapply(levels(gene_partition),function(module){
  FeaturePlot_custom(value = cell_block[,module], coord = visual_space, value_name = "Module Score",title_name = sprintf("Module %s (%d genes)",module, sum(gene_partition == module))) + scale_color_gradient(limits = c(0, 1),low = "lightgrey", high = "blue")
})
names(pl_module) = levels(gene_partition)
legend_module <- get_legend(pl_module[[1]])
prow <- cowplot::plot_grid(plotlist = lapply(pl_module,function(x) x + theme(legend.position="none")), ncol = 10)
p = cowplot::plot_grid(prow, legend_module, rel_widths = c(10, 1))
ggsave(filename = "fig-moduletsne.png", plot = p, width = 30, height = 18)
```

>>>>

# SupFig - Bone-marrow Cell Embedding
```{r}
coldef = setNames(colorRampPalette(brewer.pal(12, "Paired"))(length(unique(cell_label))),unique(cell_label))
p = DimPlot(tiss, group.by = "cell_ontology_class",label = FALSE, cols = coldef) + guides(color = guide_legend(ncol = 1,override.aes = list(size = 3))) + labs(title = NULL)

ggsave(filename = "supfig-bonemarrow.png", plot = p, width = 8, height = 5, dpi = 300)
# 
# centroids <- aggregate(. ~ cell_label, data = as.data.frame(Embeddings(tiss, "tsne")), FUN = mean)
# p <- DimPlot(tiss, group.by = "cell_ontology_class",label = FALSE, cols = coldef) + theme_void() + NoLegend() + ggtitle("Bone Marrow FACS")
# p = p + 
#   geom_text_repel(data = centroids, aes(x = tSNE_1, y = tSNE_2, label = cell_label, color = cell_label),
#                    box.padding = 0.3, point.padding = 0.3, segment.color = 'grey50',max.overlaps = 100)
```

@@

P_ls = Obtain_Pls(W = W, max_time = 2^10)
rho = Rowwise_normalize(dat[,colnames(W)])
res = fast_calculate_multi_score(W = W, init_state = rho, P_ls = P_ls)
```
```{r}
# Plot knn graph
p = plot_knn_graph(affinity_m = W, layout = visual_space)
ggsave(filename = "fig-pipeline1.png", plot = p, width = 6, height = 5, dpi = 300)
```
```{r}
# Check Diffusion KL pattern for several genes
# good gene: Igll1,Fcnb # garbage marker: Fkbp1b, Tnks1bp1, Magi2,Uchl4
genes = c("Igll1","Tnks1bp1") 
# genes_label = c("localized","non_localized")
check_time = c(0,2^3,2^10,2^15)
p = Visualize_score_pattern(res, genes = genes, add_point = check_time)

ggsave(filename = "fig-pipeline2.png", plot = p, width = 8, height = 5)

# Check Gene Diffusion on Cell graph by time
pl = lapply(1:length(genes),function(i){
  gene = genes[i]
  FeaturePlot_diffusion(coord = visual_space,init_state = rho[gene,],P_ls = P_ls,W = W,check_time = check_time,gene_name = gene,gene_color = scales::hue_pal()(2)[i])
})
p = as.ggplot(pl[[1]]) / as.ggplot(pl[[2]] & labs(title = NULL))
ggsave(filename = "fig-pipeline3.png", plot = p, width = 16, height = 8)
```

@@

df_auc = df_auc %>% filter(gt_set %in% c("Top100","CellMarkerDB")) %>% filter(!Method %in% "HighlyVariableGenes")
df_auc$Method <- with(df_auc, reorder(Method, -AUROC, FUN = median))
df_auc$gt_set <- factor(df_auc$gt_set,levels = c("CellMarkerDB","Top100"))
levels(df_auc$gt_set) = c("Criterion1 - CellMarkerDB","Criterion2 - MaxFC")
df_auc$Tissue = factor(df_auc$Tissue,levels = tissue_ls)
levels(df_auc$Tissue) = c("Bone Marrow","Pancreas","Lung")
# Create the plot
fig <- ggplot(df_auc, aes(x = Tissue, y = AUROC, fill = Method)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(AUROC, 2)), position = position_dodge(width = 0.85), vjust = -0.25, size = 3) +
  labs(x = "Tissue", y = "AUROC", fill = "Method") + coord_cartesian(ylim = c(0.5, 1)) +
  theme(legend.position = "bottom")  +  scale_fill_manual(values= coldef[names(coldef)%in%df_auc$Method]) + facet_wrap(~gt_set)
fig = fig + theme(
          legend.title = element_text(size = 20),
          legend.text = element_text(size = 15),
          axis.title.x = element_text(size = 15),
          axis.title.y = element_text(size = 15),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 10),
          panel.grid = element_blank(),
          axis.line = element_line(colour = "black"),
          panel.background = element_blank(),
          strip.background = element_rect(fill = "white", color = "white") ,
          strip.text = element_text(size = 15, color = "black"))

@@

df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))
method_vs = "lmd"
method_vs_set = c("wilcox_default","hotspot","marcopolo","semi","haystack")
```
```{r}
sub = do.call(c,lapply(method_vs_set,function(method){
  sub = c(which(df_benchmark[,method] <= 100 & df_benchmark[,method_vs] > 500),
          which(df_benchmark[,method] > 500 & df_benchmark[,method_vs] <= 100) )
  sub
}))
df_label_all = df_benchmark[unique(sub),c(method_vs,method_vs_set)]
# df_label_all$'legend' = sapply(seq(nrow(df_label_all)),function(i){
#   paste(paste(method_fullname[colnames(df_label_all)],df_label_all[i,],sep = ":"),collapse = "\n")
# })
g = c("Cd19","Naaa","Mogat2","Tifa","Abca13","Zf12","Il2rb","Phgdh","Vpreb2","Fyb")
names(g) = rep(method_vs_set,each = 2)
pl = lapply(1:length(g),function(i){
  x = g[i]
  subtitle = sprintf("%s:%d, %s:%d",method_fullname[method_vs],df_label_all[x,method_vs],method_fullname[names(g)[i]],df_label_all[x,names(g)[i]])
  color_label = ifelse(df_label_all[x,method_vs] > df_label_all[x,names(g)[i]],"red","blue")
  FeaturePlot(tiss,features = x,order =TRUE) + labs(color = "Expression") + labs(title = x,subtitle = subtitle) + 
    theme(
      plot.title = element_text(face="bold", size = 30,color = color_label),
      plot.subtitle = element_text(size = 20),
      legend.title = element_text(size = 20),
      legend.text = element_text(size = 15),
      axis.title = element_blank(),
      axis.text = element_blank(),
      axis.ticks=element_blank(),
      axis.line = element_blank())
  # + annotation_custom(grob = grid::textGrob(df_label_all[x,"legend"], x = 1, y = 1, just = c("right", "top"),gp = grid::gpar(col = "red", fontsize = 10)))
})
pl = pl[order(seq(length(g))%%2,decreasing = TRUE)]
pl[[1]] = pl[[1]] + labs(y = "Favored by LMD") + theme(axis.title.y = element_text(size = 20,face="bold", colour = "blue"))
pl[[(length(pl)/2)+1]] = pl[[(length(pl)/2)+1]] + labs(y = "Favored by Other methods") + theme(axis.title.y = element_text(size = 20,face="bold", colour = "red"))

fig = wrap_plots(pl,nrow = 2)

ggsave(filename = "fig-ranking_comparison2.png", plot = fig, width = 25, height = 10)
```
```{r}
pl_rank = lapply(method_vs_set,function(method){
  df_label = data.frame(df_benchmark[,c(method,method_vs)],label = rownames(df_benchmark))
  fullmethod = method_fullname[method]
  fullmethodvs = method_fullname[method_vs]
  df_label[c(which(df_label[,method] <= 100 & df_label[,method_vs] > 500)),"color"] = fullmethod
  df_label[c(which(df_label[,method] > 500 & df_label[,method_vs] <= 100) ),"color"] = fullmethodvs
  df_label$'color' = as.factor(df_label$'color')
  rank_cor = cor(log(df_label[,1:2],10))[1,2]
  colnames(df_label)[1:2] = c("x","y")
  p = ggplot(df_label, aes(x=x, y=y,color = color)) + geom_point(size = 1) + 
  scale_color_manual(values = c("red","blue","grey50"),
                     breaks = c(fullmethod,fullmethodvs),
                     labels = c("Favored by LMD","Favored by Other methods")) + 
    geom_abline(intercept = 0, slope = 1, col = "grey", linetype = "dashed") + 
    scale_x_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) +
    scale_y_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) + 
    expand_limits(x = c(1, 10^4), y = c(1, 10^4)) +
    labs(x = paste0(method_fullname[method]," Rank"), 
         y = paste0(method_fullname[method_vs]," Rank"),
         color = "Highlighted Genes",
         title = paste("cor =", round(rank_cor, 2)))
  # annotate gene labels
  p = p + ggrepel::geom_text_repel(data = df_label %>% filter(!is.na(color)) %>% filter(label %in% g), aes(label=label),min.segment.length = unit(0, 'lines'),nudge_y = -0.5,show.legend = FALSE,size = 5)
  p = p + theme(
    plot.title = element_text(size = 15),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"))
})
for(i in 2:length(pl_rank)){
  pl_rank[[i]] <- pl_rank[[i]] + theme(axis.title.y=element_blank())
}
p = (wrap_plots(pl_rank,nrow = 1) & theme(legend.position="bottom")) + plot_layout(guides = "collect")

ggsave(filename = "fig-ranking_comparison1.png", plot = p, width = 25, height = 6)
```

@@

baseline = score_measure %>% filter(Method == "All genes") %>%.$DensityIndex
max_x = score_measure %>% filter(Method!="All genes") %>%.$TopGene %>% max()

line_type = replace(coldef,names(coldef),"solid")
line_type["Seurat v3 Wilcoxon unfiltered"] = "twodash"
line_type["All genes"] = "dashed"

fig = ggplot(score_measure %>% filter(Method!="All genes"), aes(x = TopGene, y = DensityIndex, color = Method, group = Method, linetype = Method),linewidth = 2) + 
  geom_line(lwd = 1) +
  scale_x_log10(breaks = 10^(2:4), labels = expression(10^2, 10^3, 10^4)) +
    # expand_limits(x = c(50, 10^4)) +
  geom_hline(aes(yintercept = baseline, color = "All genes", linetype = "All genes")) +
  scale_color_manual(values= c(coldef[names(coldef)%in%score_measure$Method],"All genes" = "black")) + 
  scale_linetype_manual(values = line_type) +
  theme(
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"))
  # geom_text_repel(data = score_measure %>%  filter(Method!="all genes") %>% group_by(Method) %>% slice_head(n = 2) %>% slice_tail(n = 1), aes(label = Method), hjust = 0)

ggsave(filename = "fig-densityindex.png", plot = fig, width = 8, height = 5)
```

# SupFig - Sensitivity Test
```{r}
## Rank Stability
score_df = read.table(paste0(path,tissue_name,"_different_knn.csv"),header = TRUE)
score_ranked <- data.frame(score_df) %>% mutate(across(everything(), rank))
base = "kNN5"

top_genes = c(50,seq(100,1000,100))
jaccard_index_bw_sets = do.call(cbind,lapply(top_genes,function(top_gene)
    {
     top_gene_ls = apply(score_ranked,2,function(x) rownames(score_ranked)[order(x)][1:top_gene])
     apply(top_gene_ls,2,function(x){
       length(intersect(x,top_gene_ls[,base]))/length(union(x,top_gene_ls[,base]))
     })
  }))
colnames(jaccard_index_bw_sets) = top_genes
df = reshape2::melt(jaccard_index_bw_sets,value.name = "JaccardIndex")
colnames(df)[1:2] = c("kNN","Top_Genes")
df$kNN = as.factor(as.numeric(gsub("kNN","",df$kNN)))
df$Top_Genes = as.factor(df$Top_Genes)

fig = ggplot(data = df, aes(x = kNN, y = JaccardIndex, group = Top_Genes, color = Top_Genes)) +
  geom_line() +
  geom_point() + labs(x = "# of kNN used", y = sprintf("Jaccard Index\n (with %s)",base),color = "Top Genes") + geom_vline(xintercept = 3, color="red", linetype="dashed") + scale_y_continuous(limits = c(0,1)) +
  theme(
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"))

ggsave(filename = "supfig-sensitivity1.png", plot = fig, width = 8, height = 5)
```
```{r}
## AUC stability
auc_df = read.table(paste0(path,tissue_name,"_sensitivity_auroc.csv"),header = TRUE)
auc_df <- auc_df %>% tidyr::pivot_longer(cols = -gt, names_to = "kNN", values_to = "AUC") %>% filter(gt %in% c("Top100","CellMarkerDB"))
auc_df$gt = factor(auc_df$gt); levels(auc_df$gt) = c("CellMarkerDB","MacFC(Top100)")
auc_df$kNN = as.factor(as.numeric(gsub("kNN","",auc_df$kNN)))

fig = ggplot(data = auc_df, aes(x = kNN, y = AUC, group = gt, color = gt)) +
  geom_line() +
  geom_point() + labs(x = "# of kNN used", y = "AUROC", color = "Gold-Standard Genesets") + scale_y_continuous(limits = c(0,1)) + theme(
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"))

ggsave(filename = "supfig-sensitivity2.png", plot = fig, width = 8, height = 5)
```

# SupFig - Gene-Gene Colocolization HeatMap
```{r}
load("./marrow_result/module_result.rdata")
source("./LMD_function.R", echo = F)
library(RColorBrewer)
library(dplyr)
module_color = setNames(colorRampPalette(brewer.pal(12, "Paired"))(nlevels(gene_partition)),levels(gene_partition))
celltype_color = setNames(colorRampPalette(brewer.pal(9, "Set1"))(length(unique(cell_label))),unique(cell_label))

p = pheatmap(as.matrix(dist),
              annotation_col = data.frame(Module = gene_partition),
              cluster_rows = gene_hree, 
              cluster_cols = gene_hree,
              ann_colors = list(Module = module_color),
              treeheight_row = 0,
              col=colorRampPalette(c("firebrick3", "white"))(99),
              show_colnames = FALSE, 
              show_rownames = FALSE,
              annotation_legend = FALSE,
              # main = paste(distance_method,
              #              clustering_method,sep = "-"),
              silent = TRUE)
p = as.ggplot(p)
ggsave(filename = "supfig-moduleheatmap.png", plot = p, width = 10, height = 10)
```

# SupFig - Module TSNE
```{r}
pl_module = lapply(levels(gene_partition),function(module){
  FeaturePlot_custom(value = cell_block[,module], coord = visual_space, value_name = "Module Score",title_name = sprintf("Module %s (%d genes)",module, sum(gene_partition == module))) + scale_color_gradient(limits = c(0, 1),low = "lightgrey", high = "blue")
})
names(pl_module) = levels(gene_partition)
p = (wrap_plots(pl_module,ncol = 10) & theme(plot.title = element_text(face="bold", size = 10),legend.title = element_text(size = 30),legend.text = element_text(size = 20))) + plot_layout(guides = "collect")

ggsave(filename = "supfig-moduletsne.png", plot = p, width = 30, height = 18)
```

# SupFig-CellType-specific Module
##  Matched on Cell Embeddings
For each cell type, select the most specific modules for visualization (maximum jaccard index)
```{r}
# Get CellType One-hot plot
pl_ct = lapply(colnames(one_hot_matrix),function(ct){
  FeaturePlot_custom(value = as.factor(one_hot_matrix[,ct]), coord = visual_space, value_name = "Indicator",title_name = ct) + scale_color_manual(values = c("0" = "lightgrey", "1" = scales::hue_pal()(1)))
})
names(pl_ct) = colnames(one_hot_matrix)

ct_module_match = apply(jaccard_index_pruned,1,function(x) colnames(jaccard_index_pruned)[which.max(x)])
ct_module_match = gsub("M","",ct_module_match)

pl <- lapply(seq(length(ct_module_match)),function(i){
    pl_module[[ct_module_match[i]]]/
    pl_ct[[names(ct_module_match)[i]]]
})

p = (wrap_plots(pl,ncol = 7) & theme(plot.title = element_text(face="bold", size = 10),legend.title = element_text(size = 15),legend.text = element_text(size = 10))) + plot_layout(guides = "collect")

ggsave(filename = "supfig-ct-specific-module1.png", plot = p, width = 3*7, height = 3*4)
```

## Jaccard Index Heatmap
```{r}
thred = 0.4
jaccard_index_pruned = jaccard_index[apply(jaccard_index,1,max) > thred,]
jaccard_index_pruned = jaccard_index_pruned[,apply(jaccard_index_pruned,2,max) > thred]

colnames(jaccard_index_pruned) = paste0("M",colnames(jaccard_index_pruned))
jaccard_index_pruned = jaccard_index_pruned[names(sort(apply(jaccard_index_pruned,1,which.max))),]
p = Visualize_jaccard_mtx(jaccard_index_pruned)
p = as.ggplot(p) + coord_fixed()
ggsave(filename = "supfig-ct-specific-module2.png", plot = p, width = 8, height = 10)
```
```{r}
# # Bipartite Plot
# jaccard_thred = 0.4
# 
# library(igraph)
# library("grid") 
# library("gridExtra") 
# 
# df_edge <- as.data.frame(as.table(jaccard_index))
# colnames(df_edge) = c("from","to","weight")
# df_edge <- subset(df_edge, weight > jaccard_thred)
# df_edge$width = ifelse(df_edge$weight > 0.8,2,0.5)
# df_node = data.frame(name=c(names(module_color),names(celltype_color)),color = c(module_color,celltype_color))
# df_node$type = ifelse(df_node$name %in% names(module_color),TRUE,FALSE)
# 
# # Define specific color for module
# rownames(df_node) = df_node$name
# ct_module = names(which(apply(jaccard_index,2,max) > jaccard_thred))
# ct_subtype_module = c(4,5,6,30,39,42,43)
# ct_multype_module = c(2,13,19,33,36,54)
# cc_module = c(16,17,18,31)
# df_node[names(module_color),"color"] = "grey"
# df_node[ct_module,"color"] = "red"
# df_node[ct_multype_module,"color"] = "purple"
# df_node[ct_subtype_module,"color"] = "yellow"
# df_node[cc_module,"color"] = "green"
# 
# g <- graph_from_data_frame(df_edge, directed=FALSE, vertices=df_node)
# V(g)$shape <- ifelse(V(g)$type, "circle", "square")
# E(g)$color <- ifelse(E(g)$weight > 0.8, "red", "grey")
# l <- layout_as_bipartite(g, types=!V(g)$type)
# 
# plot(g, layout=l, vertex.size=2, vertex.label=ifelse(V(g)$type, V(g)$name, NA), vertex.frame.color = NA, asp=0.2, 
#      vertex.label.cex=0.5,
#      vertex.label.dist=-1,
#      vertex.label.degree=pi/2)
# 
# # Create Node Legend & Edge Legend
# color_label = c("green" = "cell cycle",purple = "multi cell type",red = "cell type",yellow = "cell subtype")
# df_node$subtype = color_label[df_node$color]
# 
# p <- ggplot(df_node %>% filter(type), aes(x = 0, y = 0,color = subtype)) + geom_point(size = 7) + scale_color_manual(values= setNames(names(color_label),color_label)) + theme_minimal() + labs(color = "Module Type") + theme(legend.direction="horizontal")
# grid.newpage()
# grid.draw(get_legend(p))
# 
# p <- ggplot(df_node %>% filter(!type), aes(x = 0, y = 0,color = name)) + geom_point(size = 7,shape = 15) + scale_color_manual(values= df_node %>% filter(!type) %>% pull(color,name)) + theme_minimal() + labs(color = "Cell Type") + theme(legend.direction="horizontal")
# grid.newpage()
# grid.draw(get_legend(p))
```

## Droplet Jaccard Comparison
```{r}
module_selected = unlist(apply(jaccard_index[rownames(jaccard_index_droplet),],1,function(x) colnames(jaccard_index)[which(x > thred)]))
module_selected = module_selected[order(as.numeric(module_selected))]

ct_selected = unique(unlist(apply(jaccard_index[rownames(jaccard_index_droplet),module_selected],2,function(x) rownames(jaccard_index_droplet)[which(x > 0.4)])))
ct_selected = names(sort(apply(jaccard_index[ct_selected,],1,which.max)))
